\documentclass[UTF8]{article}
\usepackage{enumerate}
\usepackage[hmargin=2cm,vmargin=2.5cm]{geometry}
\usepackage[colorlinks=true]{hyperref}
\usepackage{url}
\usepackage{etaremune}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage[dvipsnames]{xcolor}
\usepackage{sectsty}
\usepackage[dvipsnames]{xcolor}


\hypersetup{
  colorlinks=True,
  linkcolor={red!50!black},
  citecolor={blue!50!black},
  urlcolor={RedOrange}}


\pagestyle{fancy}
\fancyhf{}
\lhead{Nicol\'as Garavito-Camargo}
\chead{Curriculum Vitae}
\rhead{\thepage}
\thispagestyle{empty}
%sectionfont{\color{}}

\fancyfoot[C]{\textit{Last updated: \today}}

\begin{document}
\begin{center}
\indent \textbf{\LARGE Nicol\'as Garavito-Camargo -- Curriculum Vitae} \\
\indent \rule{17cm}{0.4pt}\\
\end{center}



\begin{center}
  Flatiron Research Fellow $|$ \href{https://www.simonsfoundation.org/flatiron/center-for-computational-astrophysics/} {Center for Computational Astrophysics
(CCA)}, NYC\\
E-mail: ngaravito@flatironinstitute.org $|$ Website:
\href{http://jngaravitoc.github.io/Garavito-Camargo}{jngaravitoc.github.io} $|$ Github: \href{http://www.github.com/jngaravitoc}{github.com/jngaravitoc}\\
\end{center}

\begin{center}
\textit{\textbf{Research Interests:} Galactic Dynamics -- Astrophysical probes
  of Dark Matter -- Computational Methods -- High-Performance Computing --
N-body Simulations -- Software development}\\
\end{center}

%Phone: +1(520)265-6092
%\section*{Research Interests}
%Galaxy Dynamics, Local Group Dynamics, Dwarf Galaxies, Galactic
%Archaeology, Astrophysical probes of Dark Matter, Galaxy Formation and Evolution.



\section*{Education}
\textbf{Ph.D.,} Astronomy and Astrophysics, \href{https://www.as.arizona.edu/}{University of Arizona}, 2021.\\
\indent \textit{Advisor: \href{https://sites.google.com/view/thebeslagroup/home}{Dr. Gurtina Besla}}\\
\textbf{M.Sc.,}  Physics, \href{https://fisica.uniandes.edu.co/en}{Universidad de Los Andes}, Bogot\'a, Colombia, 2015.\\
\indent \textit{Advisor: \href{http://wwwprof.uniandes.edu.co/~je.forero/}{Dr. Jaime E. Forero-Romero}}\\
\textbf{B.Sc.,} Physics,
\href{https://unal.edu.co/en.html}{Universidad Nacional de Colombia}, Bogot\'a, Colombia, 2013.\\
\indent \textit{Advisor:
\href{https://www.iau.org/administration/membership/individual/16146/}{Dr.
Rigoberto A. Casas Miranda}}


\section*{Appointment}
\indent Flatiron Research Fellow, Flatiron Institute, October 2021-May 2024.\\
\indent Assistant professor Universidad de La Serena, May 2024.

\section*{Scholarships and Awards}


\begin{itemize}
  \setlength\itemsep{0.0em}
  \renewcommand\labelitemi{$\cdot$}

\item University of Arizona, Theoretical Astrophysics Program, Graduate Student
Research Prize 2021.
\item University of Arizona College of Science award for Excellence in
Service for graduate students, 2020.\\ 
\indent \textit{(Awarded to one graduate student across the college of
science per year.)}
\item University of Arizona theory travel grant, 2016, 2018. 
\item McCarthy-Stoeger Scholarship 2015-2017, Vatican Observatory.
\end{itemize}
%SpaceArt scholarship, Bogot\'a Planetarium: For developing art and science material for children, 2014. \\
%Best research project at the Gaia Summer school, UNAM, Mexico City, 2013.
%2010 - $1^{st}$ Place Maloka (interactive Science Museum) contest to design a 
%didactic physics experiments.\\


\section*{Students supervision}

Total students advised or co-advised 7 (denoted by \dag); 4 Ph.D, 3 undergraduates.
Elise Darragh-Ford\dag (Graduate student at Stanford); Fall 2023-present. Silvio
Varela\dag (Graduate student at Universdad de la Serena); Fall 2022-present.
Arpit Arora\dag (Graduate student at University of Pennsylvania); Fall
2021-present. Hayden Foote\dag (Graduate student at University of Arizona); Fall 2021 - present.  Andrew Eden (Undergraduate at Florida Institute of Technology); Fall 2022-present. Ludia Adhikary (Undergraduate CUNY); Summer 2022-Summer 2023. Stephanie Carolina Cely Rodriguez (Undergraduate at Universidad Nacional de Colombia) Summer 2022-Summer 2023.




\subsection*{Academic Service} 

\begin{itemize}
  \setlength\itemsep{0.0em}
  \renewcommand\labelitemi{$\cdot$}
\item Local and Science organizing committee of the \href{https://events.simonsfoundation.org/event/1f18ba51-d6da-414f-b492-9590f29ad048/summary}{Milky Clouds over Manhattan conference}. 
\item PhD. thesis committee of Dr. Silvio Varela (University of La Serena, Chile), Nov-2023. 
\item Referee for: Astrophysical Journal (ApJ), Monthly Notices of the Royal  Astronomical Society (MNRAS), Nature, Nature Astronomy, Galaxies Journal.
\item Beyond-BFE collaboration coordinator: I lead the cosmological simulation group, organize in person and online meetings.
\item Mentor at the City University of New York CUNY-CCA program for undergraduate students at CUNY working with mentors at the CCA, summer 2022. 
\end{itemize}

\section*{Scientific Talks}

47 Total: 14 (Conferences), 33 (Seminars) 18 Invited (denoted by \dag), 26 in North America, 6 in Europe, 9 in Latin America, 1 Asia.\\



\section*{Grants}
\begin{itemize}
\setlength\itemsep{0.0em}
\renewcommand\labelitemi{$\cdot$}
\item LSSTC Grant Award (Virtual Internship in Rubin/LSST Science to Provide Research Experience to Undergraduate Students in Colombian Institutions)
  \href{https://lsstdiscoveryalliance.org/programs/science-catalyst-grants/2021/}{2021-51},
  2021. CO-PI: Nicol\'as Garavito-Camargo. This grant was awarded to support undergraduate research summer projects. 
\item International Astronomical Union (IAU) Office of Astronomy development
  (OAD)
  \href{https://www.astro4dev.org/category/a-virtual-community-mentorship-program-for-development-in-colombia/}{grant
  2021}. PI: Nicol\'as Garavito-Camargo. This grant was awarded to support the \href{https://www.astroreca.org/en/mentoring}{mentorship program for undergraduate students} in Colombia. 
\item University of Arizona theory travel grant, 2016 and 2018. 
\item IAU travel grant, 2016.
\end{itemize}

%%%%%%%%%%%%%%  Professional Experience %%%%%%%%%%%%%%%%%%5

\section*{Diversity, Equity, Inclusion (DEI) and outreach:}


\subsection*{DEI Leadership:}
\begin{itemize}
  \setlength\itemsep{0.0em}
  \renewcommand\labelitemi{$\cdot$}
\item Co-creator of the 10-week
  \href{https://recastronomia.github.io/internship/}{RECA internship program}
  for astronomy students in Colombia. May-August 2021.
\item Co-creator of the \href{https://recastronomia.github.io/mentores/}{RECA mentorship program} for astronomy students in Colombia. 2020-present.
  (The mentorship program pairs up students with professional astronomers to
  provide guidance through the application process to graduate programs)
\item Co-organizer,
  \href{https://www.as.arizona.edu/diversity_coffee/}{Diversity Journal Club} Steward Observatory, 2018-2021.
\item Creator, \href{https://astrocharlas.github.io/}{Astrocharlas},
Steward Observatory, 2018-present.
 (Spanish outreach series talks in astronomy)
\item Writer for \href{https://astrobitos.org/}{Astrobitos}, 2018-present.
\item Mentor, Tucson Initiative for Minority Engagement in Science and Technology Program \href{https://lavinia.as.arizona.edu/~timestep/}{TIMESTEP}, 2016-2018.
\end{itemize}


\section*{Research highlights in the news}

%ADD DATES *** authors and details and links
\begin{itemize}
  \setlength\itemsep{0.0em}
  \renewcommand\labelitemi{$\cdot$}
  \item Sky \& Telescope: How our largest dwarf galaxy keeps other in line
  \item JPL Nasa: Astronomers Release New All-Sky Map of Milky Way’s Outer Reaches
  \item Syfy Wire: Dark Matter could be powering a galaxy that orbits the Milky Way until they collide
  \item Astrobites: 
  \item Phys.org: Astronomers release new all-sky map of the Milky Way's outer reaches
 \item University of Arizona news: Astrophysicist help chart dark matters invisible ocean
 \item AAS NOVA 2020: An Asymmetric Dark Matter Halo
 \item AAS NOVA 2019: Hunting for a Dark Matter Wake

\end{itemize}

%%%%%%%%%%%%%%% Publications %%%%%%%%%%%%%%%%%%%%%

%## Group first author and second authors paper were I have significant %contributions (Emily's and Hayden's as a student lead paper). Also students.


\section*{Summary of publications:}



\noindent \href{https://orcid.org/0000-0001-7107-1744}{ORCID},
\href{https://ui.adsabs.harvard.edu/search/q=docs(library%2F0X5_bcuLT4iE-6-Nko0kmg)&sort=date%20desc%2C%20bibcode%20desc&p_=0}{ADS},
\href{https://arxiv.org/search/?query=garavito-camargo&searchtype=all}{arXiv}\\
refereed: 23 -- first author: 5 -- Student lead: 1  -- $h-$index: 11 -- citations : 831 (as of Jan 15th/2023) 



\end{document}



