\documentclass[14pt]{article}
\usepackage{enumerate}
\usepackage[hmargin=2cm,vmargin=2cm]{geometry}
\usepackage[colorlinks=true]{hyperref}
\usepackage{url}
\usepackage{etaremune}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage[dvipsnames]{xcolor}
\usepackage{sectsty}
\usepackage{cmtt}

\usepackage[T1]{fontenc}


\hypersetup{
  colorlinks=True,
  linkcolor={red!50!black},
  citecolor={blue!50!black},
  urlcolor={Purple}}


\pagestyle{fancy}
\fancyhf{}
\lhead{Nicol\'as Garavito-Camargo}
\chead{Curriculum Vitae}
\rhead{\thepage}
\thispagestyle{empty}
%sectionfont{\color{}}

\fancyfoot[C]{\textit{Last updated: \today}}

\begin{document}
\begin{center}
\indent \textbf{\LARGE Nicol\'as Garavito-Camargo -- Curriculum Vitae} \\
\indent \rule{17cm}{0.4pt}\\
\end{center}

\fontsize{11}{11}\selectfont

\begin{center}
  NFHP Einstein Fellow $|$
  \href{https://www.astro.umd.edu/}
  {University of Maryland}, College Park, MD\\
E-mail: nico.garavito@gmail.com $|$ Website: \href{http://jngaravitoc.github.io/Garavito-Camargo}{jngaravitoc.github.io} $|$ Github: \href{http://www.github.com/jngaravitoc}{github.com/jngaravitoc}\\
\end{center}

\begin{center}
\textit{\textbf{Research Interests:} Galactic Dynamics -- Astrophysical probes
  of Dark Matter -- Computational Methods -- High-Performance Computing --
N-body Simulations -- Software development}\\
\end{center}

%Phone: +1(520)265-6092
%\section*{Research Interests}
%Galaxy Dynamics, Local Group Dynamics, Dwarf Galaxies, Galactic
%Archaeology, Astrophysical probes of Dark Matter, Galaxy Formation and Evolution.



\section*{Appointments}

\noindent NFHP Einstein Fellow, University of Maryland, September 2025 - August 2028. 


\section*{Education and past positions}

\indent Barbara Pichardo Future Faculty Fellow, University of Arizona, February 2025-August 2025. \\

\indent Flatiron Research Fellow, Flatiron Institute, October 2021-December 2024.\\

\textbf{Ph.D.,} Astronomy and Astrophysics, \href{https://www.as.arizona.edu/}{University of Arizona}, 2021.\\
\indent \textit{Advisor: \href{https://sites.google.com/view/thebeslagroup/home}{Dr. Gurtina Besla}}\\

\textbf{M.Sc.,}  Physics, \href{https://fisica.uniandes.edu.co/en}{Universidad de Los Andes}, Bogot\'a, Colombia, 2015.\\
\indent \textit{Advisor: \href{http://wwwprof.uniandes.edu.co/~je.forero/}{Dr. Jaime E. Forero-Romero}}\\

\textbf{B.Sc.,} Physics,
\href{https://unal.edu.co/en.html}{Universidad Nacional de Colombia}, Bogot\'a, Colombia, 2013.\\
\indent \textit{Advisor:
\href{https://www.iau.org/administration/membership/individual/16146/}{Dr.
Rigoberto A. Casas Miranda}}



\section*{Scholarships and Awards}


\begin{itemize}
  \setlength\itemsep{0.0em}
  \renewcommand\labelitemi{$\cdot$}

\item NFHP Einstein Fellow, University of Maryland, September 2025-August 2028. 
\item Barbara Pichardo Future Faculty Fellowship, University of Arizona, 2025--2027. 
\item University of Arizona, Theoretical Astrophysics Program, Graduate Student
Research Prize 2021.
\item University of Arizona College of Science award for Excellence in
Service for graduate students, 2020.\\ 
\indent \textit{(Awarded to one graduate student across the college of
science per year.)}
\item University of Arizona theory travel grant, 2016, 2018. 
\item McCarthy-Stoeger Scholarship 2015-2017, Vatican Observatory.
\end{itemize}
%SpaceArt scholarship, Bogot\'a Planetarium: For developing art and science material for children, 2014. \\
%Best research project at the Gaia Summer school, UNAM, Mexico City, 2013.
%2010 - $1^{st}$ Place Maloka (interactive Science Museum) contest to design a 
%didactic physics experiments.\\


\section*{Student Supervision}
I have had the privilege of advising or co-advising a total of eight students
(five Ph.D., three undergraduates) from diverse backgrounds. 


\begin{itemize}
  \setlength\itemsep{0.0em}
  \renewcommand\labelitemi{$\cdot$}
  \item \textbf{Richard Brooks} (Graduate Student at University College
    London), Spring 2024 - present. I am advising Richard on one research project that
    was submitted for publication to ApJ (see article 29 in the publications
    section). We are currently working on a second paper, expected for
    submission in Fall 2025.
  \item \textbf{Elise Darragh-Ford} (Graduate student at Stanford), Fall 2023-Summer
    2024. I advised Elise on a research project that was the final chapter of her Ph.D. thesis, 
    resulting in one paper currently under preparation.  
  \item \textbf{Silvio Varela} (Graduate student at Universidad de la Serena), Fall 2022-present. I am currently 
    co-advising Silvio on a research project that will lead to a paper now in preparation.
  \item \textbf{Arpit Arora} (Graduate student at University of Pennsylvania);
    Fall 2021-present. I am currently co-advising (now Dr.) Arpit on two
    research projects: one paper has been accepted to ApJ (see article 27 in
    the publications section), and another was submitted in Spring 2025 (see
    article 33 in the publication section).
  \item \textbf{Hayden Foote} (Graduate student at University of Arizona), Fall
    2021--present. I co-advised Hayden on a research project that resulted in a
    submitted publication (see article 28 in the publications section), and a second paper 
    is currently in preparation.
  \item \textbf{Andrew Eden} (Undergraduate at Florida Institute of Technology),
    Fall 2022-Fall 2023. I advised Andrew on his undergraduate thesis project which
    will result in a paper that is currently in preparation. All the code that
    Andrew developed for his project is publicly available on \href{https://github.com/aeden2019/rubin_mw_mocks}{Github}. 
  \item \textbf{Ludia Adhikary} (Undergraduate CUNY), supervised through the AstroCOM CUNY/CCA program; NYC Summer 2022-Summer 2023. Ludia
    presented her work at the CCA symposium and she presented two posters. One
    at the SACNAS conference in 2022 and one at the winter AAS of 2023. 
  \item \textbf{Stephanie Carolina Cely Rodriguez} (Undergraduate at Universidad
    Nacional de Colombia), I advised undergraduate Stephanie on her undergraduate thesis as part of the
   RECA summer program in  Summer 2022. Stephanie successfully graduated in
   Summer 2023. A talk contribution from Stephanie was given at the RECA
   symposium and can be watched \href{https://www.youtube.com/watch?v=5SeOW060m24&t=1774s}{here}.
\end{itemize}

\section*{Teaching Experience}

Principal lecturer of 3 courses for undergraduate level in physics for a total
of 180 hours of teaching time. Teaching assistant for 3 courses.

\begin{itemize}
  \setlength\itemsep{0.0em}
  \renewcommand\labelitemi{$\cdot$}
\item Guest Lecturer for the graduate Galaxies class, Columbia University, Fall 2022.
\item Teaching assistant for the Astronomy Tutoring for Majors \& Minors Program. University of Arizona, Spring 2019. 
\item Teaching assistant for the Computational Physics class PHYS305. University of Arizona. Spring 2018.
\item 3 times Lecturer of the \href{https://github.com/ComputoCienciasUniandes/HerramientasComputacionales}{Computational
  Tools} at Universidad de los Andes, spring semester 2014 - spring 2015.
\item 3 times Lecturer of the Computational Methods Laboratory at Universidad de los Andes, semester spring 2014 - spring 2015.
\item Teaching assistant of the
  \href{https://github.com/ComputoCienciasUniandes/MetodosComputacionales}{Computational
  Methods} Universidad de los Andes, fall semester 2014.
\item Lecturer (for 3 different sessions) of the class Physics I Laboratory at Universidad de los Andes, fall semester 2013.
\end{itemize}


\subsection*{Academic Service} 

\begin{itemize}
  \setlength\itemsep{0.0em}
  \renewcommand\labelitemi{$\cdot$}

\item Lead coordinator of the EXP collaboration. I coordinate the cosmological
  simulations working group. I am in charge of 3 graduate students. Other responsibilities include: organizing in-person meetings twice a year.
\item Science organizing committee of the  \href{https://benasque.org/new_general/cgi-bin/years.pl?ano=2026}{Clouds over
  the Pyrenees} conference to be held in Benasque, Spain from September 6-9, 2026. 
  \item Science organizing committee of the XMC workshop in Yellowstone to be held
  in May 26th-30th 2025, at the University of Montana. 
\item Local and Science organizing committee of the \href{https://events.simonsfoundation.org/event/1f18ba51-d6da-414f-b492-9590f29ad048/summary}{Milky Clouds over Manhattan conference}. 
\item Ph.D.\ thesis committee of Dr.\ Silvio Varela (University of La Serena, Chile), Nov-2023. 
\item Referee for: Astrophysical Journal (ApJ), Monthly Notices of the Royal  Astronomical Society (MNRAS), Nature, Nature Astronomy, Astronomy and
  Astrophysics (A\&A), and the Galaxies Journal.
\item Beyond-BFE collaboration coordinator: I lead the cosmological simulation group, organize in-person and online meetings.
\item Mentor at the City University of New York CUNY-CCA program for undergraduate students at CUNY working with mentors at the CCA, summer 2022. 
\item Proposal reviewer for \href{https://clubesdeciencia.co/}{Colombian Science Clubs}, 2018.
\item Local Organizing Committee of the \href{http://forero.github.io/AndeanCosmologySchool/}{Andean Cosmology School}, Universidad de Los Andes, 2015.
\item Organizer of the student astronomy seminar at the Planetarium of Bogot\'a, 2014-2015.
\end{itemize}


\section*{Diversity, Equity, Inclusion (DEI) and outreach leadership:}


\subsection*{DEI Leadership:}

I have worked extensively to build supportive communities. I co-created a support network for astronomy students in Colombia, \href{https://www.astroreca.org/}{RECA}, which has grown to 478 members, making it the largest student association in astronomy in Latin America. In 2020, I established a yearly mentorship program designed to support students in their careers. To date, we have worked with 141 students, each paired with a senior mentor for guidance. Additionally, we have compiled valuable resources, including career panels with guest speakers and online guides for applying to PhD programs. I have also secured funding to run this program through the IAU.


\begin{itemize}
  \setlength\itemsep{0.0em}
  \renewcommand\labelitemi{$\cdot$}
\item Co-creator of the 10-week
  \href{https://recastronomia.github.io/internship/}{RECA internship program}
  for astronomy students in Colombia. May-August 2021.
\item Co-creator of the \href{https://recastronomia.github.io/mentores/}{RECA mentorship program} for astronomy students in Colombia. 2020-2024.
  (The mentorship program pairs up students with professional astronomers to
  provide guidance through the application process to graduate programs)
\item Career panelist for CUNY undergraduates in STEM ``an initiative to enable
  low-income, talented domestic students to pursue successful careers in
  promising STEM fields" organized by Professor Viviana Acquaviva. December 3rd 2021.  
\item Co-organizer,
  \href{https://www.as.arizona.edu/diversity_coffee/}{Diversity Journal Club} Steward Observatory, 2018-2021.
\item Creator, \href{https://astrocharlas.github.io/}{Astrocharlas},
Steward Observatory, 2018-2021.
 (Spanish outreach series talks in astronomy)
\item Writer for \href{https://astrobitos.org/}{Astrobitos}, 2018-2021.
\item Mentor, Tucson Initiative for Minority Engagement in Science and Technology Program \href{https://lavinia.as.arizona.edu/~timestep/}{TIMESTEP}, 2016-2018.
\end{itemize}

\subsection*{Outreach}
\begin{itemize}
  \setlength\itemsep{0.0em}
  \renewcommand\labelitemi{$\cdot$}
\item NYC Prison outreach program at MDC Brooklyn. Led 2 sessions in 2024 of 3-hour outreach
  session with Spanish-speaking women and men. Program organizer: Kiyan Tavangar (U. Columbia) 
\item Astronomy podcast in Spanish \href{https://cosmoquest.org/x/visioncosmica/nuestro-equipo/}{vision
  cosmica}. I participated in 20 episodes talking about various topics of
  astronomy for non-specialist audiences. 
\item Classroom astronomer, NOAO Project \href{https://www.noao.edu/education/astro/}{ASTRO}, 2018-2019.
\item Discussion leader, NOAO \href{http://www.teenastronomycafe.org/}{Teen Astronomy Cafe}, 2018.
\item Planetarium SpaceArt mentor for Children, Bogot\'a, Colombia, 2013-2014.
%\indent\indent Unconscious Bias Workshop, 2017. \\
\end{itemize}



\subsection*{Open source and HPC experience}

\begin{itemize}
  \setlength\itemsep{0.0em}
  \renewcommand\labelitemi{$\cdot$}
  \item Core developer and active contributor of the python packages:
    (Core developer) \href{https://github.com/EXP-code/EXP_tools}{EXPtools}, 
    (Core developer) \href{https://github.com/jngaravitoc/nba}{NBA}, Cranes. 
    (Contributor) \href{https://github.com/athob/py-ananke}{py-Ananke},
    (Contributor) \href{https://gala.adrian.pw/en/latest/}{gala},
    (Contributor) \href{https://bitbucket.org/awetzel/halo_analysis/src/master/}{halo analysis},
    (Contributor) \href{https://bitbucket.org/awetzel/gizmo_analysis/src/master/}{gizmo analysis}.
  \item Expertise with HPC N-body codes: Gadget-3, 4, EXP (CPU \& GPU), AREPO.  

\end{itemize}
\section*{Scientific Talks}

58 Total: 28 Invited (denoted by \dag)\\


\subsection*{Conferences (19)}

\begin{itemize}
  \setlength\itemsep{0.0em}
  \renewcommand\labelitemi{$\cdot$}

\item NASA Fellowship Hubble Program conference, Baltimore, October 2025. \dag
  \item \href{https://indico.ific.uv.es/event/7815/}{Valencia Workshop on the Small-Scale Structure of the Universe
    and Self-Interacting Dark Matter}, Valencia, June 2025.
\item \href{https://sites.google.com/view/xmciiworkshop/home}{XMC II Clouds over Yellowstone}, University of Montana, May 2025.
\item KITP workshop ``Dark Matter Theory, Simulation, and Analysis in the Era of Large Surveys'', UC Santa Barbara, June 2024. \dag
\item The Milky Way is not an island, Sexten, February, 2024. 
\item Surveying the Milky Way: The Universe at our backyard. Caltech,
  Pasadena, October, 2023.
\item Friends of Friends meeting, Cordoba, Argentina, April, 2023. \dag
\item IAU 379: Dynamical masses of local group galaxies, contributed talk, March, 2023.
\item \href{https://www.mso.anu.edu.au/~yting/Malaysia_IAU/}{IAU 377: Early Disk-Galaxy Formation
from JWST to the Milky Way}, contributed talk, February, 2023.
\item \href{https://accefyn.com/microsites/nodos/astroco/congreso-colombiano-de-astronomia-cocoa-2022%E2%80%8B/}{Colombian Congress of Astronomy}, Plenary talk, August, 2022. \dag
\item \href{http://fof.oac.uncor.edu/2022/}{Friends of friends meeting}, Cordoba, Argentina, April, 2022.
\item \href{https://aas.org/meetings/dda52}{Division on Dynamical Astronomy}, Virtual meeting, May 2021.
\item \href{https://stellarstreams.org/streams21/}{Streams 21}, Virtual
  Conference, February 2021. 
\item  \href{https://www.stsci.edu/contents/events/stsci/2020/april/the-local-group-assembly-and-evolution?page=2&filterUUID=6fedb8a7-}{The Local Group: Assembly and Evolution}, virtual conference, August 2020.
\item \href{https://eas.unige.ch/EAS2020/}{European Astronomical Society meeting}, virtual meeting, June 2020.
\item Durham University, UK, \href{http://astro.dur.ac.uk/cosmodwarfs/}{Small Galaxies Cosmic Questions}, August, 2019.
\item MPIA, Heidelberg, \href{http://www.mpia.de/homes/stellarhalos2018-loc/sh2018/index.html}{Stellar halos across the cosmos}, July 2018.
\item LARIM, Cartagena, Colombia, October 2016.
\item EWASS, Geneve, Switzerland, July 2014.
\end{itemize}
  
\subsection*{Seminars and Colloquia (39)}
\begin{itemize}
  \setlength\itemsep{0.0em}
  \renewcommand\labelitemi{$\cdot$}

\item OSU colloquium, Center for Astrophysics, Harvard University, February 2026.\dag 
\item ITC colloquium, Center for Astrophysics, Harvard University, January 2026.\dag 
\item Galaxies Journal Club, STScI, November 2025.\dag 
\item CTC seminar, University of Maryland, April 2025.\dag 
\item UC Santa Barbara, seminar, June 2024. \dag
\item KITP UC Santa Barbara, seminar, June 2024. \dag
\item UC Riverside, seminar, October 2023. \dag
\item Universidad de La Serena, La Serena, Chile, May 2023. \dag 
\item Instituto de Astronom\'ia y F\'isica del Espacio (IAFE), Buenos Aires, April, 2023.
\item Max Planck Institute for Astrophysics, Cosmology Seminar, March, 2023.
\item U. Rutgers, Astronomy Seminar, Nov, 2022. \dag
\item U. Columbia, Lunch talk, Sept, 2022. \dag
\item STScI, galaxies lunch talk, May, 2022. \dag
\item Universidad de Ant\'ioquia, seminar, February, 2022. \dag 
\item University of Massachusetts, Amherst, Colloquium, Jan, 2022. \dag
\item University of Madison-Wisconsin, Science seminar, November 2021.\dag
\item University of Michigan, Galaxies group seminar, November 2021.\dag
\item NYU, CCPP, seminar, November 2021.\dag 
\item CCA, Flatiron Institute, Lunch Talk, October, 2021.
\item Steward Observatory, Theoretical Astrophysics Program (TAP) colloquium, September, 2021.\dag
\item \href{https://comscicon.com/comscicon-en-espa%C3%B1ol-2021}{ComSciCon},
    June 2021. \dag
\item Steward Observatory, Galaxy lunch talk, March, 2021.
\item Universidad de los Andes, Astronomy Seminar, February, 2021. 
\item UC Irvine, Astronomy Seminar, January, 2021. \dag
\item Steward Observatory, Early Career Scientist talk, December, 2020. \dag
\item CCAPP, Seminar, December, 2020. \dag
\item Princeton, Journal Club, November 2020. \dag
\item KIPAC, Stanford, Tea-Talk, October 2020.
\item Harvard Center for Astrophysics, GCSP seminar, October 2020.
\item Carnegie Observatories, seminar, October 2020. \dag
\item University of California Berkeley, lunch talk, September 2020. 
\item The Royal Observatory of Edinburgh, UK, Coffee Talk, August 2019. \dag
\item W.M. Keck Observatory, Journal Club, June 2019.
\item Magellanic Cloud Fest III, University of Arizona, May, 2019.
\item JILA Seminar, JILA Institute, University of Colorado, December 2017.
\item STScI Galaxies Journal Club. December 2016.
\item Magellanic Cloud Fest II, University of Arizona, March 2016.
\item UNAM, Mexico City, Mexico, Nov 2013. 
\item Centro de Investigaciones De Astronom\'ia CIDA, Merida, Venezuela, July 2013.
\end{itemize}

\section*{Telescope and HPC time Awarded}
\begin{itemize}
  \setlength\itemsep{0.0em}
  \renewcommand\labelitemi{$\cdot$}
\item Hubble Space Telescope, 32 orbits, Cycle 31, 2023. PI: Prof. Sukanya Chakrabarti (U. Alabama). 
\item MareNostrum supercomputer, 1.7 million CPU hours, AECT-2023-2-0016, 2023.
  PI: Prof. Chervin Laporte (U Barcelona). 
\item GMRT 60 hours cycle 44, 2023. PI: Prof. Karin Menendez-Delmestre (Valongo Observatory, Rio de Janeiro).
\item Blanco Telescope, ``\textit{A VISTA-DECam Experiment in Near-Field
  Cosmology: Search for the Magellanic Dark Matter Wake}" cycle 2020B. PI: Prof. Julio
  Chaname (Universidad Catolica de Chile), 3 nights.
\end{itemize}


\section*{Grants}
\begin{itemize}
\setlength\itemsep{0.0em}
\renewcommand\labelitemi{$\cdot$}
\item LSSTC Grant Award (Virtual Internship in Rubin/LSST Science to Provide Research Experience to Undergraduate Students in Colombian Institutions)
  \href{https://lsstdiscoveryalliance.org/programs/science-catalyst-grants/2021/}{2021-51},
  2021. CO-PI: Nicol\'as Garavito-Camargo. This grant was awarded to support undergraduate research summer projects. 
\item International Astronomical Union (IAU) Office of Astronomy development
  (OAD)
  \href{https://www.astro4dev.org/category/a-virtual-community-mentorship-program-for-development-in-colombia/}{grant
  2021}. PI: Nicol\'as Garavito-Camargo. This grant was awarded to support the \href{https://www.astroreca.org/en/mentoring}{mentorship program for undergraduate students} in Colombia. 
\item University of Arizona theory travel grant, 2016 and 2018. 
\item IAU travel grant, 2016.
\end{itemize}

\section*{Observing Experience}
\begin{itemize}
  \setlength\itemsep{0.0em}
  \renewcommand\labelitemi{$\cdot$}
    \item DECam, Blanco-4m telescope, CTIO, Chile, 3 nights, 2020.
    \item VATT telescope. Mt Graham, Arizona, 4 nights, 2016.
    \item CIDA, Merida, Venezuela - 2 nights, 2013.
\end{itemize}
%%%%%%%%%%%%%%  Professional Experience %%%%%%%%%%%%%%%%%%5


\section*{Research highlights in the news}

%ADD DATES *** authors and details and links
\begin{itemize}
  \setlength\itemsep{0.0em}
  \renewcommand\labelitemi{$\cdot$}
  \item
    \href{https://phys.org/news/2025-02-supermassive-black-hole-large-magellanic.html}{Phys.org: There
    could be a supermassive black hole in the Large Magellanic Cloud hurling
  stars at the Milky Way}.
  \item Sky \& Telescope: How our largest dwarf galaxy keeps others in line
  \item JPL Nasa: Astronomers Release New All-Sky Map of Milky Way’s Outer Reaches
  \item Syfy Wire: Dark Matter could be powering a galaxy that orbits the Milky Way until they collide
  \item Phys.org: Astronomers release new all-sky map of the Milky Way's outer reaches
 \item University of Arizona news: Astrophysicists help chart dark matter's invisible ocean
 \item AAS NOVA 2020: An Asymmetric Dark Matter Halo
 \item AAS NOVA 2019: Hunting for a Dark Matter Wake

\end{itemize}

%%%%%%%%%%%%%%% Publications %%%%%%%%%%%%%%%%%%%%%

\section*{Publications list}

Refereed: 33 -- First author: 5 -- Supervised students: 3 (denoted by \dag) -- Total citations: 1541 (as of March 02, 2026)

\noindent \href{https://orcid.org/0000-0001-7107-1744}{ORCID},
\href{https://ui.adsabs.harvard.edu/search/q=docs(library%2F0X5_bcuLT4iE-6-Nko0kmg)&sort=date%20desc%2C%20bibcode%20desc&p_=0}{ADS},
\href{https://arxiv.org/search/?query=garavito-camargo&searchtype=all}{arXiv},
\href{https://scholar.google.com/citations?user=QDLiOFYAAAAJ&hl=en&oi=ao}{Google Scholar}\\

\subsection*{In press}

\begin{etaremune}
\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2026arXiv260100946F/abstract}{Mapping the Distorted Dark Matter Distribution of the LMC-SMC System Prior to Milky Way Infall with Basis Function Expansions}}\\
  {\small \color{darkgray} Foote, Hayden R.; Rathore, Himansh; Besla, Gurtina; \textbf{Garavito-Camargo, Nicolás}; Patel, Ekta; Petersen, Michael S.; Weinberg, Martin D.; Gómez, Facundo A.; Laporte, Chervin F. P..\\
  arXiv e-prints, January 2026. [1 citations]}

\item \dag\ \textit{\href{https://ui.adsabs.harvard.edu/abs/2025arXiv251102031D/abstract}{Shaping the Milky Way. II. The dark matter halo's response to the LMC's passage in a cosmological context}}\\
  {\small \color{darkgray} Darragh-Ford, Elise; \textbf{Garavito-Camargo, Nicolas}; Arora, Arpit; Wechsler, Risa H.; Mansfield, Phil; Besla, Gurtina; Petersen, Michael S.; Weinberg, Martin D.; Varela-Lavin, Silvio; Buch, Deveshi; et al..\\
  arXiv e-prints, November 2025. [3 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2025arXiv251102231L/abstract}{Stellar Birth Radii in the LMC: Insights into Chemodynamics, Radial Migration, and Star Formation Across the Disk}}\\
  {\small \color{darkgray} Lu, Yuxi; Garver, Bethany; Nidever, David L.; Povick, Joshua T.; \textbf{Garavito-Camargo, Nicolás}; Cioni, Maria-Rosa L.; Horta, Danny.\\
  arXiv e-prints, November 2025. [0 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2025arXiv251004735B/abstract}{The Milky Way - Large Magellanic Cloud Interaction with Simulation Based Inference}}\\
  {\small \color{darkgray} Brooks, Richard A. N.; Sanders, Jason L.; Chandra, Vedant; \textbf{Garavito-Camargo, Nicolás}; Dillamore, Adam M.; Price-Whelan, Adrian M.; Ting, Yuan-Sen.\\
  arXiv e-prints, October 2025. [3 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2025arXiv250217565D/abstract}{Where do High-Velocity Dark Matter Particles come from in the Milky Way?}}\\
  {\small \color{darkgray} DeBrae, Aidan; Behroozi, Peter; \textbf{Garavito-Camargo, Nicolas}.\\
  arXiv e-prints, February 2025. [2 citations]}

\end{etaremune}

\subsection*{First author and student-led publications}

\begin{etaremune}
\item \dag\ \textit{\href{https://ui.adsabs.harvard.edu/abs/2025ApJ...988..190A/abstract}{Shaping the Milky Way: The Interplay of Mergers and Cosmic Filaments}}\\
  {\small \color{darkgray} Arora, Arpit; \textbf{Garavito-Camargo, Nicolás}; Sanderson, Robyn E.; Weinberg, Martin D.; Petersen, Michael S.; Varela-Lavin, Silvio; Gómez, Facundo A.; Johnston, Kathryn V.; Laporte, Chervin F. P.; Shipp, Nora; et al..\\
  The Astrophysical Journal, August 2025. [15 citations]}

\item \dag\ \textit{\href{https://ui.adsabs.harvard.edu/abs/2025ApJ...978...79B/abstract}{LMC Calls, Milky Way Halo Answers: Disentangling the Effects of the MW--LMC Interaction on Stellar Stream Populations}}\\
  {\small \color{darkgray} Brooks, Richard A. N.; \textbf{Garavito-Camargo, Nicolás}; Johnston, Kathryn V.; Price-Whelan, Adrian M.; Sanders, Jason L.; Lilleengen, Sophia.\\
  The Astrophysical Journal, January 2025. [17 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2024ApJ...975..100G/abstract}{On the Corotation of Milky Way Satellites: LMC-mass Satellites Induce Apparent Motions in Outer Halo Tracers}}\\
  {\small \color{darkgray} \textbf{Garavito-Camargo, Nicolás}; Price-Whelan, Adrian M.; Samuel, Jenna; Cunningham, Emily C.; Patel, Ekta; Wetzel, Andrew; Johnston, Kathryn V.; Arora, Arpit; Sanderson, Robyn E.; Garrison, Lehman; et al..\\
  The Astrophysical Journal, November 2024. [16 citations]}

\item \dag\ \textit{\href{https://ui.adsabs.harvard.edu/abs/2024ApJ...974..286A/abstract}{LMC-driven Anisotropic Boosts in Stream--Subhalo Interactions}}\\
  {\small \color{darkgray} Arora, Arpit; \textbf{Garavito-Camargo, Nicolás}; Sanderson, Robyn E.; Cunningham, Emily C.; Wetzel, Andrew; Panithanpaisal, Nondh; Barry, Megan.\\
  The Astrophysical Journal, October 2024. [17 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2021ApJ...923..140G/abstract}{The Clustering of Orbital Poles Induced by the LMC: Hints for the Origin of Planes of Satellites}}\\
  {\small \color{darkgray} \textbf{Garavito-Camargo, Nicolás}; Patel, Ekta; Besla, Gurtina; Price-Whelan, Adrian M.; Gómez, Facundo A.; Laporte, Chervin F. P.; Johnston, Kathryn V..\\
  The Astrophysical Journal, December 2021. [38 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2021ApJ...919..109G/abstract}{Quantifying the Impact of the Large Magellanic Cloud on the Structure of the Milky Way's Dark Matter Halo Using Basis Function Expansions}}\\
  {\small \color{darkgray} \textbf{Garavito-Camargo, Nicolás}; Besla, Gurtina; Laporte, Chervin F. P.; Price-Whelan, Adrian M.; Cunningham, Emily C.; Johnston, Kathryn V.; Weinberg, Martin; Gómez, Facundo A..\\
  The Astrophysical Journal, October 2021. [125 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2019ApJ...884...51G/abstract}{Hunting for the Dark Matter Wake Induced by the Large Magellanic Cloud}}\\
  {\small \color{darkgray} \textbf{Garavito-Camargo, Nicolas}; Besla, Gurtina; Laporte, Chervin F. P.; Johnston, Kathryn V.; Gómez, Facundo A.; Watkins, Laura L..\\
  The Astrophysical Journal, October 2019. [208 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2014ApJ...795..120G/abstract}{The Impact of Gas Bulk Rotation on the Ly$\alpha$ Line}}\\
  {\small \color{darkgray} \textbf{Garavito-Camargo, Juan N.}; Forero-Romero, Jaime E.; Dijkstra, Mark.\\
  The Astrophysical Journal, November 2014. [11 citations]}

\end{etaremune}

\subsection*{Publications as collaborator}

\begin{etaremune}
\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2026MNRAS.545f2111B/abstract}{A simulation-based inference approach to the dynamics of the MW--LMC system - validation}}\\
  {\small \color{darkgray} Brooks, Richard A. N.; Sanders, Jason L.; Dillamore, Adam M.; \textbf{Garavito-Camargo, Nicolás}; Price-Whelan, Adrian M..\\
  Monthly Notices of the Royal Astronomical Society, January 2026. [8 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2025ApJ...988..156C/abstract}{All-sky Kinematics of the Distant Halo: The Reflex Response to the LMC}}\\
  {\small \color{darkgray} Chandra, Vedant; Naidu, Rohan P.; Conroy, Charlie; \textbf{Garavito-Camargo, Nicolas}; Laporte, Chervin; Bonaca, Ana; Cargile, Phillip A.; Cunningham, Emily; Han, Jiwon Jesse; Johnson, Benjamin D.; et al..\\
  The Astrophysical Journal, August 2025. [32 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2025ApJ...985..121P/abstract}{The M31--M33 Interaction: Impact on M31's Center-of-mass Motion and Satellite Orbits}}\\
  {\small \color{darkgray} Patel, Ekta; \textbf{Garavito-Camargo, Nicolás}; Escala, Ivanna.\\
  The Astrophysical Journal, May 2025. [4 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2025ApJ...983..151C/abstract}{The All-sky Impact of the LMC on the Milky Way Circumgalactic Medium}}\\
  {\small \color{darkgray} Carr, Christopher; Bryan, Greg L.; \textbf{Garavito-Camargo, Nicolás}; Besla, Gurtina; Setton, David J.; Johnston, Kathryn V.; Su, Kung-Yi.\\
  The Astrophysical Journal, April 2025. [4 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2025ApJ...983...83C/abstract}{The Distant Milky Way Halo from the Southern Hemisphere: Characterization of the LMC-induced Dynamical Friction Wake}}\\
  {\small \color{darkgray} Cavieres, Manuel; Chanamé, Julio; Navarrete, Camila; Ordenes-Briceño, Yasna; \textbf{Garavito-Camargo, Nicolás}; Besla, Gurtina; Hempel, Maren; Vivas, A. Katherina; Gómez, Facundo.\\
  The Astrophysical Journal, April 2025. [10 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2025ApJ...982..188H/abstract}{Hypervelocity Stars Trace a Supermassive Black Hole in the Large Magellanic Cloud}}\\
  {\small \color{darkgray} Han, Jiwon Jesse; El-Badry, Kareem; Lucchini, Scott; Hernquist, Lars; Brown, Warren; \textbf{Garavito-Camargo, Nico}; Conroy, Charlie; Sari, Re'em.\\
  The Astrophysical Journal, April 2025. [18 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2025ApJ...979..171F/abstract}{Segue 2 Recently Collided with the Cetus-Palca Stream: New Opportunities to Constrain Dark Matter in an Ultra-faint Dwarf}}\\
  {\small \color{darkgray} Foote, Hayden R.; Besla, Gurtina; \textbf{Garavito-Camargo, Nicolás}; Patel, Ekta; Thomas, Guillaume F.; Bonaca, Ana; Price-Whelan, Adrian M.; Peter, Annika H. G.; Zaritsky, Dennis; Conroy, Charlie.\\
  The Astrophysical Journal, February 2025. [3 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2024ApJ...977...23A/abstract}{Efficient and Accurate Force Replay in Cosmological-baryonic Simulations}}\\
  {\small \color{darkgray} Arora, Arpit; Sanderson, Robyn; Regan, Christopher; \textbf{Garavito-Camargo, Nicolás}; Bregou, Emily; Panithanpaisal, Nondh; Wetzel, Andrew; Cunningham, Emily C.; Loebman, Sarah R.; Dropulic, Adriana; et al..\\
  The Astrophysical Journal, December 2024. [15 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2024JOSS....9.6234T/abstract}{Generating synthetic star catalogs from simulated data for next-gen observatories with py-ananke}}\\
  {\small \color{darkgray} Thob, Adrien; Sanderson, Robyn; Eden, Andrew; Nikakhtar, Farnik; Panithanpaisal, Nondh; \textbf{Garavito-Camargo, Nicolás}; Sharma, Sanjib.\\
  The Journal of Open Source Software, October 2024. [6 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2024ApJ...971...69D/abstract}{Dark Matter Distribution in Milky Way analog Galaxies}}\\
  {\small \color{darkgray} de Isídio, Natanael G.; Menéndez-Delmestre, K.; Gonçalves, T. S.; Grossi, M.; Rodrigues, D. C.; \textbf{Garavito-Camargo, N.}; Araujo-Carvalho, A.; Beaklini, P. P. B.; Cavalcante-Coelho, Y.; Cortesi, A.; et al..\\
  The Astrophysical Journal, August 2024. [7 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2024A&A...683A..47G/abstract}{Galactoseismology in cosmological simulations. Vertical perturbations by dark matter, satellite galaxies, and gas}}\\
  {\small \color{darkgray} García-Conde, B.; Antoja, T.; Roca-Fàbrega, S.; Gómez, F.; Ramos, P.; \textbf{Garavito-Camargo, N.}; Gómez-Flechoso, M. A..\\
  Astronomy and Astrophysics, March 2024. [11 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2024MNRAS.527.9810H/abstract}{The proto-galaxy of Milky Way-mass haloes in the FIRE simulations}}\\
  {\small \color{darkgray} Horta, Danny; Cunningham, Emily C.; Sanderson, Robyn; Johnston, Kathryn V.; Deason, Alis; Wetzel, Andrew; McCluskey, Fiona; \textbf{Garavito-Camargo, Nicolás}; Necib, Lina; Faucher-Giguère, Claude-André; et al..\\
  Monthly Notices of the Royal Astronomical Society, February 2024. [28 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2023JCAP...10..070S/abstract}{The impact of the Large Magellanic Cloud on dark matter direct detection signals}}\\
  {\small \color{darkgray} Smith-Orlik, Adam; Ronaghi, Nima; Bozorgnia, Nassim; Cautun, Marius; Fattahi, Azadeh; Besla, Gurtina; Frenk, Carlos S.; \textbf{Garavito-Camargo, Nicolás}; Gómez, Facundo A.; Grand, Robert J. J.; et al..\\
  Journal of Cosmology and Astroparticle Physics, October 2023. [30 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2023ApJ...954..163F/abstract}{Structure, Kinematics, and Observability of the Large Magellanic Cloud's Dynamical Friction Wake in Cold versus Fuzzy Dark Matter}}\\
  {\small \color{darkgray} Foote, Hayden R.; Besla, Gurtina; Mocz, Philip; \textbf{Garavito-Camargo, Nicolás}; Lancaster, Lachlan; Sparre, Martin; Cunningham, Emily C.; Vogelsberger, Mark; Gómez, Facundo A.; Laporte, Chervin F. P..\\
  The Astrophysical Journal, September 2023. [24 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2023MNRAS.523.5853V/abstract}{Lopsided galaxies in a cosmological context: a new galaxy-halo connection}}\\
  {\small \color{darkgray} Varela-Lavin, Silvio; Gómez, Facundo A.; Tissera, Patricia B.; Besla, Gurtina; \textbf{Garavito-Camargo, Nicolás}; Marinacci, Federico; Laporte, Chervin F. P..\\
  Monthly Notices of the Royal Astronomical Society, August 2023. [15 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2023ApJ...942...18C/abstract}{Implications of the Milky Way Travel Velocity for Dynamical Mass Estimates of the Local Group}}\\
  {\small \color{darkgray} Chamberlain, Katie; Price-Whelan, Adrian M.; Besla, Gurtina; Cunningham, Emily C.; \textbf{Garavito-Camargo, Nicolás}; Peñarrubia, Jorge; Petersen, Michael S..\\
  The Astrophysical Journal, January 2023. [32 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2022ApJ...939....2A/abstract}{On the Stability of Tidal Streams in Action Space}}\\
  {\small \color{darkgray} Arora, Arpit; Sanderson, Robyn E.; Panithanpaisal, Nondh; Cunningham, Emily C.; Wetzel, Andrew; \textbf{Garavito-Camargo, Nicolás}.\\
  The Astrophysical Journal, November 2022. [38 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2021Natur.592..534C/abstract}{All-sky dynamical response of the Galactic halo to the Large Magellanic Cloud}}\\
  {\small \color{darkgray} Conroy, Charlie; Naidu, Rohan P.; \textbf{Garavito-Camargo, Nicolás}; Besla, Gurtina; Zaritsky, Dennis; Bonaca, Ana; Johnson, Benjamin D..\\
  Nature, April 2021. [127 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2020ApJ...898....4C/abstract}{Quantifying the Stellar Halo's Response to the LMC's Infall with Spherical Harmonics}}\\
  {\small \color{darkgray} Cunningham, Emily C.; \textbf{Garavito-Camargo, Nicolas}; Deason, Alis J.; Johnston, Kathryn V.; Erkal, Denis; Laporte, Chervin F. P.; Besla, Gurtina; Luger, Rodrigo; Sanderson, Robyn E..\\
  The Astrophysical Journal, July 2020. [65 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2020ApJ...893..121P/abstract}{The Orbital Histories of Magellanic Satellites Using Gaia DR2 Proper Motions}}\\
  {\small \color{darkgray} Patel, Ekta; Kallivayalil, Nitya; \textbf{Garavito-Camargo, Nicolas}; Besla, Gurtina; Weisz, Daniel R.; van der Marel, Roeland P.; Boylan-Kolchin, Michael; Pawlowski, Marcel S.; Gómez, Facundo A..\\
  The Astrophysical Journal, April 2020. [184 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2019JCAP...11..013B/abstract}{The highest-speed local dark matter particles come from the Large Magellanic Cloud}}\\
  {\small \color{darkgray} Besla, G.; Peter, A. H. G.; \textbf{Garavito-Camargo, N.}.\\
  Journal of Cosmology and Astroparticle Physics, November 2019. [43 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2018MNRAS.481..286L/abstract}{The influence of Sagittarius and the Large Magellanic Cloud on the stellar disc of the Milky Way Galaxy}}\\
  {\small \color{darkgray} Laporte, Chervin F. P.; Johnston, Kathryn V.; Gómez, Facundo A.; \textbf{Garavito-Camargo, Nicolas}; Besla, Gurtina.\\
  Monthly Notices of the Royal Astronomical Society, November 2018. [225 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2018ApJ...863..144S/abstract}{The Extremely Luminous Quasar Survey in the Sloan Digital Sky Survey Footprint. II. The North Galactic Cap Sample}}\\
  {\small \color{darkgray} Schindler, Jan-Torge; Fan, Xiaohui; McGreer, Ian D.; Yang, Jinyi; Wang, Feige; Green, Richard; \textbf{Garavito-Camargo, Nicolas}; Huang, Yun-Hsin; O'Donnell, Christine; Patej, Anna; et al..\\
  The Astrophysical Journal, August 2018. [21 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2018MNRAS.474...12F/abstract}{Modelling the gas kinematics of an atypical Ly $\alpha$ emitting compact dwarf galaxy}}\\
  {\small \color{darkgray} Forero-Romero, Jaime E.; Gronke, Max; Remolina-Gutiérrez, Maria Camila; \textbf{Garavito-Camargo, Nicolás}; Dijkstra, Mark.\\
  Monthly Notices of the Royal Astronomical Society, February 2018. [2 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2018MNRAS.473.1218L/abstract}{Response of the Milky Way's disc to the Large Magellanic Cloud in a first infall scenario}}\\
  {\small \color{darkgray} Laporte, Chervin F. P.; Gómez, Facundo A.; Besla, Gurtina; Johnston, Kathryn V.; \textbf{Garavito-Camargo, Nicolas}.\\
  Monthly Notices of the Royal Astronomical Society, January 2018. [142 citations]}

\end{etaremune}

\section*{White papers}

\begin{etaremune}
\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2023arXiv230611784H/abstract}{NANCY: Next-generation All-sky Near-infrared Community surveY}}\\
  {\small \color{darkgray} Han, Jiwon Jesse; Dey, Arjun; Price-Whelan, Adrian M.; Najita, Joan; Schlafly, Edward F.; Saydjari, Andrew; Wechsler, Risa H.; Bonaca, Ana; Schlegel, David J; Conroy, Charlie; et al..\\
  arXiv e-prints, June 2023. [9 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2022arXiv220802781B/abstract}{From Data to Software to Science with the Rubin Observatory LSST}}\\
  {\small \color{darkgray} Breivik, Katelyn; Connolly, Andrew J.; Ford, K. E. Saavik; Jurić, Mario; Mandelbaum, Rachel; Miller, Adam A.; Norman, Dara; Olsen, Knut; O'Mullane, William; Price-Whelan, Adrian; et al..\\
  arXiv e-prints, August 2022. [14 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2019BAAS...51c.489D/abstract}{Mass Spectroscopy of the Milky Way}}\\
  {\small \color{darkgray} Dey, Arjun; Najita, Joan R.; Koposov, Sergey; Rockosi, Connie; Li, Ting; Olsen, Knut; Allende Prieto, Carlos; Bonaca, Ana; Besla, Gurtina; \textbf{Garavito-Camargo, Nicolas}; et al..\\
  Bulletin of the American Astronomical Society, May 2019. [1 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2019BAAS...51c.347S/abstract}{The Multidimensional Milky Way}}\\
  {\small \color{darkgray} Sanderson, Robyn; Carlin, Jeff; Cunningham, Emily; \textbf{Garavito-Camargo, Nicolas}; Guhathakurta, Puragra; Johnston, Kathryn; Laporte, Chervin; Li, Ting; Sohn, S. Tony; Anderson, Jay; et al..\\
  Bulletin of the American Astronomical Society, May 2019. [7 citations]}

\end{etaremune}


\end{document}
