\documentclass[letterpaper]{article}
\usepackage{enumerate}
\usepackage[hmargin=2cm,vmargin=2.5cm]{geometry}
\usepackage{hyperref}
\usepackage{url}
\begin{document}

\begin{center}
\textsc{\LARGE Juan Nicol\'as Garavito Camargo}\\
\textsc{\large Curriculum Vitae}\\
\end{center}

\textsc{\Large Contact Information:}\\

Steward Observatory, 933 North Cherry Av. Tucson, AZ.\\
\indent \textbf{email:}jngaravitoc[at]email [dot] arizona [dot] edu\\
\indent Personal web page:
\url{jngaravitoc.github.io/Garavito-Camargo}\\
\indent Github: \url{www.github.com/jngaravitoc} \\

\textsc{\Large Education:}\\

University of Arizona, Tucson, Arizona.\\
\indent Ph.D., Astronomy and Astrophysics (expected
graduation date: 2020).\\
\indent Advisor: Dr. Gurtina Besla\\

University of Los Andes, Bogot\'a, Colombia.\\
\indent M.Sc., Physics, 2015.\\
\indent Advisor: Dr. Jaime E. Forero-Romero\\

National University of Colombia, Bogot\'a, Colombia.\\
\indent B.Sc., Physics, 2013.\\
\indent Advisor: Dr. Rigoberto A. Casas Miranda\\

\textsc{\Large Research Interests:}\\

Galaxy Dynamics, Local Group dynamics, Galaxy Formation and evolution.\\


\textsc{\Large Fellowships, grants \& Awards:}\\
\begin{itemize}
\setlength\itemsep{0em}
\item University of Arizona theory travel grant (2016). \\
\item IAU travel grant (2016).\\
\item McCarthy-Stoeger scholarship (2015-2017).\\
\item SpaceArt scholarship Bogot\'a Planetarium: For developing art and science material for children (2014). \\
\item Best project at GAIA summer school held at Mexico City (2013).\\
%2010 - $1^{st}$ Place Maloka (interactive Science Museum) contest to design a didactical physics experiment.\\
\end{itemize}

\textsc{\Large Publications:}\\

As a first author:\\
\begin{enumerate}
\item \textit{The impact of gas bulk rotation on the morphology of the
Lyman-alpha line}. \textbf{Garavito-Camargo J.N} ,Forero-Romero J.E, Dijkstra M. ApJ, 795, 120, (2014).\\
\end{enumerate}


As n-th author:\\

\begin{enumerate}
\item  \textit{Response of the Milky Way's disc to the Large Magellanic Cloud in
a first infall scenario.} Laporte, C., Gomez, F., Besla,G., Kathryn V.
Johnston \& \textbf{Nicolas Garavito-Camargo}. MNRAS submitted.\\
\end{enumerate}


%\textsc{\Large Congresses \& Meetings:}\\
%$\left[6\right]$ Satellite galaxies and dwarfs in the local group. Leibniz Institute for Astrophysics, Potsdam, Germany. \indent \indent \ \ \ \ \ \
%\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ 08/2014  \\
%$\left[5\right]$ European Week of Astronomy and Space Science EWASS.  \indent \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ 07/2014 \\
%$\left[4\right]$ XIV Latin American Regional IAU Meeting (LARIM), Florianopolis, Brasil.  11/2013
%\normalsize {(Poster Contribution: 'Effects of the gas bulk Rotation on the morphology of the Ly $\alpha$ line')}\\
%$\left[3\right]$\large{ Fifth Venezuelan Astronomy Reunion (RVA), Merida, Venezuela. \indent \ \ \ \  \ \ \ \ \ \ \ \ \ \ \ \ 12/2012}
%\normalsize{(Talk Contribution: 'Effect of the rotation of distant galaxies on the Lyman-alpha emission line'.)}\\
%$\left[2\right]$\large{ Colombian Congress in Astronomy (COCOA), Bucaramanga, Colombia. \indent \ \ 11/2012}
%\normalsize{(Poster Contribution: Study Of The Dynamical Friction Time-Scale Using N-body Simulations.)}\\
%$\left[1\right]$\large{ XVII National Physics Congress, Santa Marta, Colombia. \indent \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \  \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \   /2009}\\


\textsc{\Large Summer Schools \& Workshops attended:}\\
%\\
\begin{enumerate}
\setlength\itemsep{0em} 
\item  \textit{Andean School on Cosmology}, University of Los Andes, 06/2015.\\
%\item \textit{CLUES meeting}, IAP Potsdam, Germany. \indent \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ 08/2014\\
\item \textit{GAIA Visualization workshop}, Viena, Austria, 07/2014.\\
%$\left[10\right]$ Vatican Observatory Summer School (VOSS).\\
%"Galaxies Near and Far, Young and Old". \indent \ \ \ \  \ \ \  \ \ \  \ \ \  \ \
% \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ 06/2014 \\
\item \textit{Galactic Dynamics in the Times of GAIA and other Great
Surveys}, Mexico City, UNAM CU, 11/2013.\\
%$\left[8\right]$ \textsc{NEBULATOM}, "A Capacity Development Workshop for Latin\\
%American Astronomers on Emission Line Objects in the Universe". \indent \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ 03/2013 \\
%Choron\'i, Venezuela.  \\
%$\left[7\right]$ III Venezuelan Astronomy School (EVA). Merida, Venezuela. \indent \ \ \ \ \ \ \ \ \ \ \ \ \ \ 12/2012\\
\item \textit{Hippac Summer School on Astrocomputing}, University of California San Diego, 07/2012 \\
%\left[5\right]$ Data reduction in Cosmology School.  \indent \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ 12/2011
%National Astronomical Observatory of Colombia.\\
%$\left[4\right]$ XVI Ciclo de cursos especiais em Astronomia.  \indent \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ 10/2011
%National Observatory of Rio de Janeiro, Brasil. \\
%$\left[3\right]$ $1^{st}$ Workshop on Statistical Physics. \indent \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ 08/2011
%National University of Colombia, Andes University, Bogot\'{a}, Colombia. \\
\item \textit{School of Numerical Relativity}, National Astronomical Observatory of Colombia, 2011.\\
\end{enumerate}
%$\left[1\right]$ Extragalactic Astrophysics School. \indent \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ /2010
%National Astronomical Observatory of Colombia.\\


\textsc{\Large Talks:}\\
\begin{enumerate}
\setlength\itemsep{0em}
\item STScI Galaxies Journal Club. 12/02/16.\\
\item ``The effect of the LMC on the MW dark matter halo:
Consequences for GAIA and astrometry", LARIM, Cartagena, Colombia,
10/03/16
\item ``The effect of the LMC on the MW dark matter halo", Magellanic Cloud Fest, 
University of Arizona, 03/23/16\\
\item ``The effect of gas bulk rotation on the Lyman Alpha line profile", EWASS, Geneve, Switzerland, July-2014.\\
\item ``GAIAs View on the metallicities of the Milky Way", UNAM, Mexico City, Mexico, Nov-2013. \\
\item A Bayesian Method to study galaxy streams in the Milky Way Disk", CIDA, Merida, Venezuela , July-2013.\\
\end{enumerate}

\textsc{\Large Observing Experience:}\\
\begin{itemize}
\item{4 Nights at the VATT telescope. Mt Graham Arizona.}
\item{2 Nights at CIDA, Merida, Venezuela.}
\end{itemize}


\textsc{\Large Teaching Experience:}\\

Physics I Laboratory: Universidad de los Andes. \indent ($2^{nd}$
Semester-2013)\\
\indent Computational Tools: Universidad de los Andes. \indent
($1^{st}$ Semester-2014)\\
\indent Computational Methods Laboratory: Universidad de los Andes.
\indent ($1^{st}$ Semester-2014)\\
\indent TA, Computational Methods: Universidad de los Andes. \indent
($1^{st}$ Semester-2014)\\
\indent Computational Tools: Universidad de los Andes. \indent
($2^{nd}$ Semester-2014)\\
\indent Computational Methods Laboratory: Universidad de los Andes.
\indent ($2^{nd}$ Semester-2014)\\
\indent TA, Computational Methods: Universidad de los Andes. \indent
($2^{nd}$ Semester-2014)\\

\textsc{\Large Public Service:}\\
\begin{itemize}
\setlength\itemsep{0em}
\item Local Organizing Committee of the Andean Cosmology School,
University of Los Andes (June 2015).
\item Organizer of the student astronomy seminar at the Planetarium of Bogot\'a (2014-2015).
\end{itemize}


\textsc{\Large Computational Skills}:\\
\\
\indent Programming Languages: Python, C, C++.\\
%visualization Software: TOPCAT, GLUE, Sphviewer.\\

\textsc{\Large Languages:}\\
\\
\indent Spanish (native), English(Fluent).

\end{document}
