\documentclass[14pt]{article}
\usepackage{enumerate}
\usepackage[hmargin=2cm,vmargin=2cm]{geometry}
\usepackage[colorlinks=true]{hyperref}
\usepackage{url}
\usepackage{etaremune}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage[dvipsnames]{xcolor}
\usepackage{sectsty}
\usepackage[T1]{fontenc}

\hypersetup{
  colorlinks=True,
  linkcolor={red!50!black},
  citecolor={blue!50!black},
  urlcolor={Purple}}

\pagestyle{fancy}
\fancyhf{}
\lhead{Nicol\'as Garavito-Camargo}
\chead{Publications}
\rhead{\thepage}
\thispagestyle{empty}

\fancyfoot[C]{\textit{Last updated: \today}}

\begin{document}
\begin{center}
\indent \textbf{\LARGE Nicol\'as Garavito-Camargo -- Publications} \\
\indent \rule{17cm}{0.4pt}\\
\end{center}

\fontsize{11}{11}\selectfont

\section*{Publications list}

Refereed: 33 -- First author: 5 -- Supervised students: 3 (denoted by \dag) -- Total citations: 1535 (as of February 26, 2026)

\noindent \href{https://orcid.org/0000-0001-7107-1744}{ORCID}, \href{https://ui.adsabs.harvard.edu/search/q=docs(library%2F0X5_bcuLT4iE-6-Nko0kmg)&sort=date%20desc%2C%20bibcode%20desc&p_=0}{ADS}, \href{https://arxiv.org/search/?query=garavito-camargo&searchtype=all}{arXiv}, \href{https://scholar.google.com/citations?user=QDLiOFYAAAAJ&hl=en&oi=ao}{Google Scholar}\\

\subsection*{In press}

\begin{etaremune}
\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2026arXiv260100946F/abstract}{Mapping the Distorted Dark Matter Distribution of the LMC-SMC System Prior to Milky Way Infall with Basis Function Expansions}}\\
  {\small \color{darkgray} Foote, Hayden R.; Rathore, Himansh; Besla, Gurtina; \textbf{Garavito-Camargo, Nicolás}; Patel, Ekta; Petersen, Michael S.; Weinberg, Martin D.; Gómez, Facundo A.; Laporte, Chervin F. P..\\
  arXiv e-prints, January 2026. [1 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2025arXiv251102231L/abstract}{Stellar Birth Radii in the LMC: Insights into Chemodynamics, Radial Migration, and Star Formation Across the Disk}}\\
  {\small \color{darkgray} Lu, Yuxi; Garver, Bethany; Nidever, David L.; Povick, Joshua T.; \textbf{Garavito-Camargo, Nicolás}; Cioni, Maria-Rosa L.; Horta, Danny.\\
  arXiv e-prints, November 2025. [0 citations]}

\item \dag\ \textit{\href{https://ui.adsabs.harvard.edu/abs/2025arXiv251102031D/abstract}{Shaping the Milky Way. II. The dark matter halo's response to the LMC's passage in a cosmological context}}\\
  {\small \color{darkgray} Darragh-Ford, Elise; \textbf{Garavito-Camargo, Nicolas}; Arora, Arpit; Wechsler, Risa H.; Mansfield, Phil; Besla, Gurtina; Petersen, Michael S.; Weinberg, Martin D.; Varela-Lavin, Silvio; Buch, Deveshi; et al..\\
  arXiv e-prints, November 2025. [3 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2025arXiv251004735B/abstract}{The Milky Way - Large Magellanic Cloud Interaction with Simulation Based Inference}}\\
  {\small \color{darkgray} Brooks, Richard A. N.; Sanders, Jason L.; Chandra, Vedant; \textbf{Garavito-Camargo, Nicolás}; Dillamore, Adam M.; Price-Whelan, Adrian M.; Ting, Yuan-Sen.\\
  arXiv e-prints, October 2025. [3 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2025arXiv250217565D/abstract}{Where do High-Velocity Dark Matter Particles come from in the Milky Way?}}\\
  {\small \color{darkgray} DeBrae, Aidan; Behroozi, Peter; \textbf{Garavito-Camargo, Nicolas}.\\
  arXiv e-prints, February 2025. [2 citations]}

\end{etaremune}

\subsection*{First author and student-led publications}

\begin{etaremune}
\item \dag\ \textit{\href{https://ui.adsabs.harvard.edu/abs/2025ApJ...988..190A/abstract}{Shaping the Milky Way: The Interplay of Mergers and Cosmic Filaments}}\\
  {\small \color{darkgray} Arora, Arpit; \textbf{Garavito-Camargo, Nicolás}; Sanderson, Robyn E.; Weinberg, Martin D.; Petersen, Michael S.; Varela-Lavin, Silvio; Gómez, Facundo A.; Johnston, Kathryn V.; Laporte, Chervin F. P.; Shipp, Nora; et al..\\
  The Astrophysical Journal, August 2025. [15 citations]}

\item \dag\ \textit{\href{https://ui.adsabs.harvard.edu/abs/2025ApJ...978...79B/abstract}{LMC Calls, Milky Way Halo Answers: Disentangling the Effects of the MW--LMC Interaction on Stellar Stream Populations}}\\
  {\small \color{darkgray} Brooks, Richard A. N.; \textbf{Garavito-Camargo, Nicolás}; Johnston, Kathryn V.; Price-Whelan, Adrian M.; Sanders, Jason L.; Lilleengen, Sophia.\\
  The Astrophysical Journal, January 2025. [17 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2024ApJ...975..100G/abstract}{On the Corotation of Milky Way Satellites: LMC-mass Satellites Induce Apparent Motions in Outer Halo Tracers}}\\
  {\small \color{darkgray} \textbf{Garavito-Camargo, Nicolás}; Price-Whelan, Adrian M.; Samuel, Jenna; Cunningham, Emily C.; Patel, Ekta; Wetzel, Andrew; Johnston, Kathryn V.; Arora, Arpit; Sanderson, Robyn E.; Garrison, Lehman; et al..\\
  The Astrophysical Journal, November 2024. [16 citations]}

\item \dag\ \textit{\href{https://ui.adsabs.harvard.edu/abs/2024ApJ...974..286A/abstract}{LMC-driven Anisotropic Boosts in Stream--Subhalo Interactions}}\\
  {\small \color{darkgray} Arora, Arpit; \textbf{Garavito-Camargo, Nicolás}; Sanderson, Robyn E.; Cunningham, Emily C.; Wetzel, Andrew; Panithanpaisal, Nondh; Barry, Megan.\\
  The Astrophysical Journal, October 2024. [17 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2021ApJ...923..140G/abstract}{The Clustering of Orbital Poles Induced by the LMC: Hints for the Origin of Planes of Satellites}}\\
  {\small \color{darkgray} \textbf{Garavito-Camargo, Nicolás}; Patel, Ekta; Besla, Gurtina; Price-Whelan, Adrian M.; Gómez, Facundo A.; Laporte, Chervin F. P.; Johnston, Kathryn V..\\
  The Astrophysical Journal, December 2021. [37 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2021ApJ...919..109G/abstract}{Quantifying the Impact of the Large Magellanic Cloud on the Structure of the Milky Way's Dark Matter Halo Using Basis Function Expansions}}\\
  {\small \color{darkgray} \textbf{Garavito-Camargo, Nicolás}; Besla, Gurtina; Laporte, Chervin F. P.; Price-Whelan, Adrian M.; Cunningham, Emily C.; Johnston, Kathryn V.; Weinberg, Martin; Gómez, Facundo A..\\
  The Astrophysical Journal, October 2021. [124 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2019ApJ...884...51G/abstract}{Hunting for the Dark Matter Wake Induced by the Large Magellanic Cloud}}\\
  {\small \color{darkgray} \textbf{Garavito-Camargo, Nicolas}; Besla, Gurtina; Laporte, Chervin F. P.; Johnston, Kathryn V.; Gómez, Facundo A.; Watkins, Laura L..\\
  The Astrophysical Journal, October 2019. [208 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2014ApJ...795..120G/abstract}{The Impact of Gas Bulk Rotation on the Ly$\alpha$ Line}}\\
  {\small \color{darkgray} \textbf{Garavito-Camargo, Juan N.}; Forero-Romero, Jaime E.; Dijkstra, Mark.\\
  The Astrophysical Journal, November 2014. [11 citations]}

\end{etaremune}

\subsection*{Publications as collaborator}

\begin{etaremune}
\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2026MNRAS.545f2111B/abstract}{A simulation-based inference approach to the dynamics of the MW--LMC system - validation}}\\
  {\small \color{darkgray} Brooks, Richard A. N.; Sanders, Jason L.; Dillamore, Adam M.; \textbf{Garavito-Camargo, Nicolás}; Price-Whelan, Adrian M..\\
  Monthly Notices of the Royal Astronomical Society, January 2026. [8 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2025ApJ...988..156C/abstract}{All-sky Kinematics of the Distant Halo: The Reflex Response to the LMC}}\\
  {\small \color{darkgray} Chandra, Vedant; Naidu, Rohan P.; Conroy, Charlie; \textbf{Garavito-Camargo, Nicolas}; Laporte, Chervin; Bonaca, Ana; Cargile, Phillip A.; Cunningham, Emily; Han, Jiwon Jesse; Johnson, Benjamin D.; et al..\\
  The Astrophysical Journal, August 2025. [32 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2025ApJ...985..121P/abstract}{The M31--M33 Interaction: Impact on M31's Center-of-mass Motion and Satellite Orbits}}\\
  {\small \color{darkgray} Patel, Ekta; \textbf{Garavito-Camargo, Nicolás}; Escala, Ivanna.\\
  The Astrophysical Journal, May 2025. [4 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2025ApJ...982..188H/abstract}{Hypervelocity Stars Trace a Supermassive Black Hole in the Large Magellanic Cloud}}\\
  {\small \color{darkgray} Han, Jiwon Jesse; El-Badry, Kareem; Lucchini, Scott; Hernquist, Lars; Brown, Warren; \textbf{Garavito-Camargo, Nico}; Conroy, Charlie; Sari, Re'em.\\
  The Astrophysical Journal, April 2025. [18 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2025ApJ...983...83C/abstract}{The Distant Milky Way Halo from the Southern Hemisphere: Characterization of the LMC-induced Dynamical Friction Wake}}\\
  {\small \color{darkgray} Cavieres, Manuel; Chanamé, Julio; Navarrete, Camila; Ordenes-Briceño, Yasna; \textbf{Garavito-Camargo, Nicolás}; Besla, Gurtina; Hempel, Maren; Vivas, A. Katherina; Gómez, Facundo.\\
  The Astrophysical Journal, April 2025. [10 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2025ApJ...983..151C/abstract}{The All-sky Impact of the LMC on the Milky Way Circumgalactic Medium}}\\
  {\small \color{darkgray} Carr, Christopher; Bryan, Greg L.; \textbf{Garavito-Camargo, Nicolás}; Besla, Gurtina; Setton, David J.; Johnston, Kathryn V.; Su, Kung-Yi.\\
  The Astrophysical Journal, April 2025. [4 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2025ApJ...979..171F/abstract}{Segue 2 Recently Collided with the Cetus-Palca Stream: New Opportunities to Constrain Dark Matter in an Ultra-faint Dwarf}}\\
  {\small \color{darkgray} Foote, Hayden R.; Besla, Gurtina; \textbf{Garavito-Camargo, Nicolás}; Patel, Ekta; Thomas, Guillaume F.; Bonaca, Ana; Price-Whelan, Adrian M.; Peter, Annika H. G.; Zaritsky, Dennis; Conroy, Charlie.\\
  The Astrophysical Journal, February 2025. [3 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2024ApJ...977...23A/abstract}{Efficient and Accurate Force Replay in Cosmological-baryonic Simulations}}\\
  {\small \color{darkgray} Arora, Arpit; Sanderson, Robyn; Regan, Christopher; \textbf{Garavito-Camargo, Nicolás}; Bregou, Emily; Panithanpaisal, Nondh; Wetzel, Andrew; Cunningham, Emily C.; Loebman, Sarah R.; Dropulic, Adriana; et al..\\
  The Astrophysical Journal, December 2024. [15 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2024JOSS....9.6234T/abstract}{Generating synthetic star catalogs from simulated data for next-gen observatories with py-ananke}}\\
  {\small \color{darkgray} Thob, Adrien; Sanderson, Robyn; Eden, Andrew; Nikakhtar, Farnik; Panithanpaisal, Nondh; \textbf{Garavito-Camargo, Nicolás}; Sharma, Sanjib.\\
  The Journal of Open Source Software, October 2024. [6 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2024ApJ...971...69D/abstract}{Dark Matter Distribution in Milky Way analog Galaxies}}\\
  {\small \color{darkgray} de Isídio, Natanael G.; Menéndez-Delmestre, K.; Gonçalves, T. S.; Grossi, M.; Rodrigues, D. C.; \textbf{Garavito-Camargo, N.}; Araujo-Carvalho, A.; Beaklini, P. P. B.; Cavalcante-Coelho, Y.; Cortesi, A.; et al..\\
  The Astrophysical Journal, August 2024. [7 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2024A&A...683A..47G/abstract}{Galactoseismology in cosmological simulations. Vertical perturbations by dark matter, satellite galaxies, and gas}}\\
  {\small \color{darkgray} García-Conde, B.; Antoja, T.; Roca-Fàbrega, S.; Gómez, F.; Ramos, P.; \textbf{Garavito-Camargo, N.}; Gómez-Flechoso, M. A..\\
  Astronomy and Astrophysics, March 2024. [11 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2024MNRAS.527.9810H/abstract}{The proto-galaxy of Milky Way-mass haloes in the FIRE simulations}}\\
  {\small \color{darkgray} Horta, Danny; Cunningham, Emily C.; Sanderson, Robyn; Johnston, Kathryn V.; Deason, Alis; Wetzel, Andrew; McCluskey, Fiona; \textbf{Garavito-Camargo, Nicolás}; Necib, Lina; Faucher-Giguère, Claude-André; et al..\\
  Monthly Notices of the Royal Astronomical Society, February 2024. [28 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2023JCAP...10..070S/abstract}{The impact of the Large Magellanic Cloud on dark matter direct detection signals}}\\
  {\small \color{darkgray} Smith-Orlik, Adam; Ronaghi, Nima; Bozorgnia, Nassim; Cautun, Marius; Fattahi, Azadeh; Besla, Gurtina; Frenk, Carlos S.; \textbf{Garavito-Camargo, Nicolás}; Gómez, Facundo A.; Grand, Robert J. J.; et al..\\
  Journal of Cosmology and Astroparticle Physics, October 2023. [30 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2023ApJ...954..163F/abstract}{Structure, Kinematics, and Observability of the Large Magellanic Cloud's Dynamical Friction Wake in Cold versus Fuzzy Dark Matter}}\\
  {\small \color{darkgray} Foote, Hayden R.; Besla, Gurtina; Mocz, Philip; \textbf{Garavito-Camargo, Nicolás}; Lancaster, Lachlan; Sparre, Martin; Cunningham, Emily C.; Vogelsberger, Mark; Gómez, Facundo A.; Laporte, Chervin F. P..\\
  The Astrophysical Journal, September 2023. [24 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2023MNRAS.523.5853V/abstract}{Lopsided galaxies in a cosmological context: a new galaxy-halo connection}}\\
  {\small \color{darkgray} Varela-Lavin, Silvio; Gómez, Facundo A.; Tissera, Patricia B.; Besla, Gurtina; \textbf{Garavito-Camargo, Nicolás}; Marinacci, Federico; Laporte, Chervin F. P..\\
  Monthly Notices of the Royal Astronomical Society, August 2023. [15 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2023ApJ...942...18C/abstract}{Implications of the Milky Way Travel Velocity for Dynamical Mass Estimates of the Local Group}}\\
  {\small \color{darkgray} Chamberlain, Katie; Price-Whelan, Adrian M.; Besla, Gurtina; Cunningham, Emily C.; \textbf{Garavito-Camargo, Nicolás}; Peñarrubia, Jorge; Petersen, Michael S..\\
  The Astrophysical Journal, January 2023. [32 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2022ApJ...939....2A/abstract}{On the Stability of Tidal Streams in Action Space}}\\
  {\small \color{darkgray} Arora, Arpit; Sanderson, Robyn E.; Panithanpaisal, Nondh; Cunningham, Emily C.; Wetzel, Andrew; \textbf{Garavito-Camargo, Nicolás}.\\
  The Astrophysical Journal, November 2022. [38 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2021Natur.592..534C/abstract}{All-sky dynamical response of the Galactic halo to the Large Magellanic Cloud}}\\
  {\small \color{darkgray} Conroy, Charlie; Naidu, Rohan P.; \textbf{Garavito-Camargo, Nicolás}; Besla, Gurtina; Zaritsky, Dennis; Bonaca, Ana; Johnson, Benjamin D..\\
  Nature, April 2021. [127 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2020ApJ...898....4C/abstract}{Quantifying the Stellar Halo's Response to the LMC's Infall with Spherical Harmonics}}\\
  {\small \color{darkgray} Cunningham, Emily C.; \textbf{Garavito-Camargo, Nicolas}; Deason, Alis J.; Johnston, Kathryn V.; Erkal, Denis; Laporte, Chervin F. P.; Besla, Gurtina; Luger, Rodrigo; Sanderson, Robyn E..\\
  The Astrophysical Journal, July 2020. [65 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2020ApJ...893..121P/abstract}{The Orbital Histories of Magellanic Satellites Using Gaia DR2 Proper Motions}}\\
  {\small \color{darkgray} Patel, Ekta; Kallivayalil, Nitya; \textbf{Garavito-Camargo, Nicolas}; Besla, Gurtina; Weisz, Daniel R.; van der Marel, Roeland P.; Boylan-Kolchin, Michael; Pawlowski, Marcel S.; Gómez, Facundo A..\\
  The Astrophysical Journal, April 2020. [183 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2019JCAP...11..013B/abstract}{The highest-speed local dark matter particles come from the Large Magellanic Cloud}}\\
  {\small \color{darkgray} Besla, G.; Peter, A. H. G.; \textbf{Garavito-Camargo, N.}.\\
  Journal of Cosmology and Astroparticle Physics, November 2019. [43 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2018MNRAS.481..286L/abstract}{The influence of Sagittarius and the Large Magellanic Cloud on the stellar disc of the Milky Way Galaxy}}\\
  {\small \color{darkgray} Laporte, Chervin F. P.; Johnston, Kathryn V.; Gómez, Facundo A.; \textbf{Garavito-Camargo, Nicolas}; Besla, Gurtina.\\
  Monthly Notices of the Royal Astronomical Society, November 2018. [224 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2018ApJ...863..144S/abstract}{The Extremely Luminous Quasar Survey in the Sloan Digital Sky Survey Footprint. II. The North Galactic Cap Sample}}\\
  {\small \color{darkgray} Schindler, Jan-Torge; Fan, Xiaohui; McGreer, Ian D.; Yang, Jinyi; Wang, Feige; Green, Richard; \textbf{Garavito-Camargo, Nicolas}; Huang, Yun-Hsin; O'Donnell, Christine; Patej, Anna; et al..\\
  The Astrophysical Journal, August 2018. [21 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2018MNRAS.474...12F/abstract}{Modelling the gas kinematics of an atypical Ly $\alpha$ emitting compact dwarf galaxy}}\\
  {\small \color{darkgray} Forero-Romero, Jaime E.; Gronke, Max; Remolina-Gutiérrez, Maria Camila; \textbf{Garavito-Camargo, Nicolás}; Dijkstra, Mark.\\
  Monthly Notices of the Royal Astronomical Society, February 2018. [2 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2018MNRAS.473.1218L/abstract}{Response of the Milky Way's disc to the Large Magellanic Cloud in a first infall scenario}}\\
  {\small \color{darkgray} Laporte, Chervin F. P.; Gómez, Facundo A.; Besla, Gurtina; Johnston, Kathryn V.; \textbf{Garavito-Camargo, Nicolas}.\\
  Monthly Notices of the Royal Astronomical Society, January 2018. [140 citations]}

\end{etaremune}

\subsection*{White papers}

\begin{etaremune}
\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2023arXiv230611784H/abstract}{NANCY: Next-generation All-sky Near-infrared Community surveY}}\\
  {\small \color{darkgray} Han, Jiwon Jesse; Dey, Arjun; Price-Whelan, Adrian M.; Najita, Joan; Schlafly, Edward F.; Saydjari, Andrew; Wechsler, Risa H.; Bonaca, Ana; Schlegel, David J; Conroy, Charlie; et al..\\
  arXiv e-prints, June 2023. [8 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2022arXiv220802781B/abstract}{From Data to Software to Science with the Rubin Observatory LSST}}\\
  {\small \color{darkgray} Breivik, Katelyn; Connolly, Andrew J.; Ford, K. E. Saavik; Jurić, Mario; Mandelbaum, Rachel; Miller, Adam A.; Norman, Dara; Olsen, Knut; O'Mullane, William; Price-Whelan, Adrian; et al..\\
  arXiv e-prints, August 2022. [14 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2019BAAS...51c.347S/abstract}{The Multidimensional Milky Way}}\\
  {\small \color{darkgray} Sanderson, Robyn; Carlin, Jeff; Cunningham, Emily; \textbf{Garavito-Camargo, Nicolas}; Guhathakurta, Puragra; Johnston, Kathryn; Laporte, Chervin; Li, Ting; Sohn, S. Tony; Anderson, Jay; et al..\\
  Bulletin of the American Astronomical Society, May 2019. [7 citations]}

\item \textit{\href{https://ui.adsabs.harvard.edu/abs/2019BAAS...51c.489D/abstract}{Mass Spectroscopy of the Milky Way}}\\
  {\small \color{darkgray} Dey, Arjun; Najita, Joan R.; Koposov, Sergey; Rockosi, Connie; Li, Ting; Olsen, Knut; Allende Prieto, Carlos; Bonaca, Ana; Besla, Gurtina; \textbf{Garavito-Camargo, Nicolas}; et al..\\
  Bulletin of the American Astronomical Society, May 2019. [1 citations]}

\end{etaremune}

\end{document}
